# Introduction

# First Section
## A Subsection Sample
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

### Sample Heading (Third Level) 
Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

#### Sample Heading (Fourth Level)
The contribution should contain no more than four levels of
headings. Table`r ref("tab1")` gives a summary of all heading levels.

Another nice feature are shortcuts for \eg and \ie 

# References
You can cite any paper in parenthesis as following [@valdez2017priming] or inline saying that @valdez2017priming found something.
Multiple citations are possible as well [@valdez2017priming;@valdez2019users].

You can refer to other sections by kebab-casing to section`r ref("a-subsection-sample")`. You can easily cite an r-package directly in the text by using the `cite_pkg` function from the package `r rmdtemplates::cite_pkg("rmdtemplates")`. 

Refer to figure `r ref("fig:fig1")`.

# Environments

The environments 'definition', 'lemma', 'proposition', 'corollary', 'remark', and 'example' are defined in the LLNCS document class as well.


## Theorems

```{r echo=FALSE, results='asis'}
theorem <- generate_environment("Theorem")
theorem("This is a sample theorem. The run-in heading is set in bold, 
        while the following text appears in italics. Definitions, lemmas, propositions, 
        and corollaries are styled the same way.")
```



## Equations
\begin{equation}
x + y = z
\end{equation}



## Tables
You can get the non breaking space in RStudio by pressing ALT+SPACE.
You can refer to tables by using Table`r ref("tab:table1")`.

```{r table1}
# Note that the label has to be added manually in the caption here.
iris %>% 
  head() %>% 
  knitr::kable(caption = "Test", booktabs = T, longtable = F) 
```


### Inline Latex Tables
You can directly add latex tables.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}


## Figures

You can refer to tables by using Figure \ref{fig:fig1}.

```{r fig1, fig.cap="This is the text caption under the figure"}
# Note that the label for a figure is always fig:chunkname
iris %>% ggplot() + aes(x = Sepal.Length) + geom_histogram() + cowplot::theme_minimal_hgrid()

```



