---
title: "Making Reproducible Research Simple using RMarkdown and the OSF"
author: "André Calero Valdez"
date: "`r Sys.Date()`"
bibliography: ["../Paper/rpackages.bib", "../bib/bibliography.bib"]
#biblio-style: "apalike"
link-citations: true
always_allow_html: yes
output:
  #bookdown::html_document2:
  rmdformats::material:
    highlight: kate
    collapsed: false
    dev: png
    self_contained: true
    number_sections: true
    code_folding: hide
    thumbnails: true
    gallery: true
    fig_width: 6
    fig_height: 3.5
    df_print: kable
    use_bookdown: true
---


```{r knitr_init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, paged.print=TRUE}
## Global options
library(knitr)
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               fig.width = 6,
               fig.height = 3.5,
               fig.retina = 2
               )
opts_knit$set(width=100)

# Load required libraries
library(rmdformats)
library(tidyverse)
library(DT)
library(rmdtemplates)
# add libraries here
#library(cowplot)
# add libraries here

# Add libraries to cite here:
pkgs <- c("knitr", "tidyverse", "rmdformats", "kableExtra", "scales", "psych", "rmdtemplates", "sdcMicro", "webshot", "here", "DiagrammeR", "citr", "drake", "esquisse", "usethis", "gramr", "questionr", "ggstatsplot")
rmdtemplates::write_bib(pkgs)
options(kableExtra.auto_format = FALSE)
```


# Abstract {-}
The replication crisis has eroded the public's trust in science. Many famous studies, even published in renowed journals, fail to produce the same results when replicated by other researchers. While this is the outcome of several problems in research, one aspect has gotten critical attention---reproducibility. The term reproducible research refers to studies that contain all materials necessary to reproduce the scientific results by other researchers. This allows other to identify flaws in calculations and improve scientific rigor. In this paper, we show a workflow for reproducible research using the R language and a set of additional packages and tools that simplify a reproducible research procedure.     

```{r child = '../rmds/10_introduction.Rmd'}
```

```{r child = '../rmds/20_research_compendium.Rmd'}
```

```{r child = '../rmds/30_open.Rmd'}
```

```{r child = '../rmds/40_drake.Rmd'}
```

```{r child = '../rmds/50_procedure.Rmd', eval = TRUE}
```

```{r child = '../rmds/60_discussion.Rmd', eval = TRUE}
```


# Data
On this sub-page you can find the data used as a downloadable file (CSV, Excel, or PDF).

```{r data_1, echo=TRUE, message=TRUE, warning=TRUE, paged.print=TRUE}
data_df <- iris



datatable(data_df, filter = list(position = 'top', clear = TRUE, plain = FALSE), extensions = c('Buttons','FixedColumns'), options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf'),
    scrollX = TRUE,
    fixedColumns = TRUE
  ))

```   




```{r r_citations2, eval=TRUE, include=TRUE, results="asis"}
#rmdtemplates::line_cite(pkgs) # This creates a single line citing all packages
rmdtemplates::list_cite(pkgs) # This creates a "thightlist" of all packages 
```

# References
